Bias no more! A practical guide to latent mean centering in multilevel models

### 2022-12-07 ms.Rmd
Figure options

```{r setup, include = FALSE}
library(papaja)
library(posterior)
library(ggdist)
library(brms)
library(tidyverse)

@@

# Save models in a directory
dir.create("models", FALSE)
```

>>>>

```{r setup, include = FALSE}
library(papaja)
library(posterior)
library(scales)
library(ggdist)
library(brms)
library(tidyverse)

@@

# Save models in a directory
dir.create("models", FALSE)

# Plotting options
theme_set(
  theme_linedraw(base_size = 9.6) +
    theme(
      strip.background = element_rect(fill = "gray90", color = "gray90"),
      strip.text = element_text(color = "black", hjust = 0),
      panel.grid = element_blank()
    )
)
```
